%-------------------------------------
% My Resume
% Author : Alex Anguiano
% License : MIT
%-------------------------------------

\documentclass[letterpaper,12pt]{article}[leftmargin=*]

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage{ifxetex}
\ifxetex
  \usepackage{fontspec}
  \usepackage[xetex]{hyperref}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{hyperref}
\fi
\usepackage{fontawesome}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{anyfontsize}
\usepackage{xcolor}
\usepackage{tabularx}

%-------------------------------------------------- SETTINGS HERE --------------------------------------------------
% Header settings
\def \fullname {Alex Anguiano}
\def \subtitle {}

\def \linkedinicon {\faLinkedin}
\def \linkedinlink {https://www.linkedin.com/in/alex-a-anguiano/}
\def \linkedintext {/alex-a-anguiano}

\def \phoneicon {\faPhone}
\def \phonetext {+1-480-335-2816}

\def \emailicon {\faEnvelope}
\def \emaillink {mailto:alexanguiano96@gmail.com}
\def \emailtext {alexanguiano96@gmail.com}

\def \githubicon {\faGithub}
\def \githublink {https://github.com/aaanguia}
\def \githubtext {/aaanguia}

\def \websiteicon {\faGlobe}
\def \websitelink {http://arcanis.xyz/}
\def \websitetext {arcanis.xyz/}

\def \headertype {\doublecol} % \singlecol or \doublecol

% Misc settings
\def \entryspacing {-0pt}

\def \bulletstyle {\faAngleRight}

% Define colours
\definecolor{primary}{HTML}{000000}
\definecolor{secondary}{HTML}{69C96E}
\definecolor{accent}{HTML}{263238}
\definecolor{links}{HTML}{399D3E}

%------------------------------------------------------------------------------------------------------------------- 

% Defines to make listing easier
\def \linkedin {\linkedinicon \hspace{3pt}\href{\linkedinlink}{\linkedintext}}
\def \phone {\phoneicon \hspace{3pt}{ \phonetext}}
\def \email {\emailicon \hspace{3pt}\href{\emaillink}{\emailtext}}
\def \github {\githubicon \hspace{3pt}\href{\githublink}{\githubtext}}
\def \website {\websiteicon \hspace{3pt}\href{\websitelink}{\websitetext}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.1in}

% Define the link colours
\hypersetup{
    colorlinks=true,
    urlcolor=links,
}

% Set the margin alignment 
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------
% Custom commands

% Sections
\renewcommand{\section}[2]{\vspace{5pt}
  \colorbox{secondary}{\color{white}\raggedbottom\normalsize\textbf{{#1}{\hspace{7pt}#2}}}
}

% Entry start and end, for spacing
\newcommand{\resumeEntryStart}{\begin{itemize}[leftmargin=2.5mm]}
\newcommand{\resumeEntryEnd}{\end{itemize}\vspace{\entryspacing}}

% Itemized list for the bullet points under an entry, if necessary
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=4.5mm]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Resume item
\renewcommand{\labelitemii}{\bulletstyle}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Entry with title, subheading, date(s), and location
\newcommand{\resumeEntryTSDL}[4]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
      \textit{\color{accent}\small#3} & \textit{\color{accent}\small#4} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry with title and date(s)
\newcommand{\resumeEntryTD}[2]{
  \vspace{-1pt}\item[]
    \begin{tabularx}{0.97\textwidth}{X@{\hspace{60pt}}r}
      \textbf{\color{primary}#1} & {\firabook\color{accent}\small#2} \\
    \end{tabularx}\vspace{-6pt}
}

% Entry for special (skills)
\newcommand{\resumeEntryS}[2]{
  \item[]\small{
    \textbf{\color{primary}#1 }{ #2 \vspace{-6pt}}
  }
}

% Double column header
\newcommand{\doublecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[c]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l@{\hspace{1.5em}}l}
        {\small#4} & {\small#1} \\
        {\small#5} & {\small#2} \\
        {\small#6} & {\small#3}
      \end{tabular}
    }
  \end{tabularx}
}

% Single column header
\newcommand{\singlecol}[6]{
  \begin{tabularx}{\textwidth}{Xr}
    {
      \begin{tabular}[b]{l}
        \fontsize{35}{45}\selectfont{\color{primary}{{\textbf{\fullname}}}} \\
        {\textit{\subtitle}} % You could add a subtitle here
      \end{tabular}
    } & {
      \begin{tabular}[c]{l}
        {\small#1} \\
        {\small#2} \\
        {\small#3} \\
        {\small#4} \\
        {\small#5} \\
        {\small#6}
      \end{tabular}
    }
  \end{tabularx}
}

\begin{document}
%-------------------------------------------------- BEGIN HERE --------------------------------------------------

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{\website}{\phone}{\email}{} % Set the order of items here
\vspace{-10pt} % Set a negative value to push the body up, and the opposite

%-------------------------------------------------- EDUCATION --------------------------------------------------
\section{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {Arizona State University}{2017 -- 2021}
      {Bachelor of Science, Software Engineering \quad Honors: cum laude }{Mesa, AZ}
  \resumeEntryEnd
  
  %-------------------------------------------------- EXPERIENCE --------------------------------------------------
\section{\faPieChart}{Experience}

  \resumeEntryStart
    \resumeEntryTSDL
      {Cognizant}{June 2021 -- Present}
      {Associate Full Stack Developer}{Dallas, TX}
    \resumeItemListStart
      \resumeItem {Completed in-house academy training over the course of 15 weeks focusing in Java Spring Boot, HTML/CSS/JS, React and AWS Deployment. Culminating to a Full-Stack Application called Tun3rs R Us, in the final few weeks of training.}
      \resumeItem {In an effort to transition the Retail-Consumer-Goods sales team from Mock-Ups and PowerPoints, three developers and I from the new hire cohorts, undertook an internal initiative to prove that new hires were able to undertake a potential client deal and create an MVP.}
      \resumeItem {Implemented and styled existing Tensor Flow Models and APIs into a React Application to be used in the Retail, Beauty, and Athletic spaces. After a successful demo and presentation to Service Line Sales Leader and Senior Vice President-Sales, I branched out on other potential client deals. Picking up React Native to utilize NFC and Geo-Locating tech to solve a location and supply chain issue a potential customer has. Moving back to our initial Tensor Flow MVP. }
      \resumeItem {After successful demo’s to our peers, I was able to accomplish the ability…. <Need some sort of resolution, was going to mention that our internal project team was officially onboarded on to RCG, or something about being funded for the rest of the year>}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
      {Joaquin Bustoz Math-Science Honors Program}{May 2019 -- Aug. 2019}
      {Academic Class Supervisor}{Tempe, AZ}
    \resumeItemListStart
      \resumeItem {Trained and oversaw five tutors and a grader to create a safe and productive learning environment for program participants.}
            \resumeItem {Maintained clear channels of communication between academic, residential, and administrative staff to guarantee student success and safety.}
    \resumeItemListEnd
  \resumeEntryEnd
  

%-------------------------------------------------- PROJECTS --------------------------------------------------
\section{\faFlask}{Projects}

 \resumeEntryStart
    \resumeEntryTD
      {Tun3rs R Us}{}
    \resumeItemListStart
      \resumeItem {A full stack E-Commerce Website built from scratch to provide high quality performance parts to tuner enthusiasts around the world.}
      \resumeItem {Utilized Springboot back end utilizing a MongoRepository that saved product items to a MongoDB Atlas Instance. Front end utilized React and media queries for the presentation layer. Utilized Axios HTTP calls that connected product items JSON to be displayed onto front end.}
        \resumeItem {Produced during my time in Academy at Cognizant. Deployed back end via Elastic Beanstalk and front end hosted on AWS Amplify.}
    \resumeItemListEnd
  \resumeEntryEnd


  \resumeEntryStart
    \resumeEntryTD
      {Fenoto Technologies Inc. UI/UX Capstone Project}{}

    \resumeItemListStart
        \resumeItem {Performed User Experience Design Cycle to create a Web/Mobile Application for Fenoto by creating User Personas, Iterating and Prototyping Designs, and implementing HTML/CSS/JS Mockups.}
        \resumeItem {Designed and programmed a Dashboard with a focus on portraying Big Data in a clean and informative fashion, and presented prototypes to the Product Manager.}
        \resumeItem {Facilitated Sprint Planning Meetings by iterating PM and Customer Feedback into our backlog, and addressed peer feedback within the team. }
    \resumeItemListEnd
  \resumeEntryEnd
  

  \resumeEntryStart
    \resumeEntryTD
      {"Interconnected Transportation Network for Sydney"}{}
    \resumeItemListStart
      \resumeItem {Eliminated traffic congestion in New South Wales by creating a new transportation network in collaboration with two other students from the University of New South Wales.}
            \resumeItem {Developed an autonomous network and charging solutions that could be implemented within 5 years.}
                  \resumeItem {Presented design solution at the Grand Challenge Scholars Program Symposium 2017.}
    \resumeItemListEnd
  \resumeEntryEnd
  
%-------------------------------------------------- PROGRAMMING SKILLS --------------------------------------------------
\section{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Technologies } {Java, Spring Boot, HTML, CSS, JavaScript, React, React Native, AWS, Agile}
 \resumeEntryEnd

\end{document}
