%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font

%------------------------------------------------

\name{Alex Anguiano}

\address{(480)~$\cdot$~335~$\cdot$~2816 \\ alexanguiano96@gmail.com} % Contact information
\address{https://www.linkedin.com/in/alex-a-anguiano/} % Contact information


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Colorado Legislative Council }{October 2022 - Present}{Associate Application Developer $\rightarrow$ Application Developer}{Denver, CO}
		\item Developing in house applications to improve the Legislative Process for the Colorado State Legislators.
		\item Utilize Typescript and Redux to provide a history based rich text editor experience with SlateJS. Developed Printing Experiences that match specific criteria to Colorado Red Books with Spring Boot. 
		\item Manage AWS Deployments, MySQL instances, and IT tickets to ensure legislative titles and documents remain up to date and are easily accessible to Legislative staff and applications.
		\item Reducing third-party overhead and administration by providing high quality in house solutions.
	\end{rSubsection}

	\begin{rSubsection}{Cognizant}{June 2021 - October 2022}{Associate Full Stack Developer}{Remote}
		\item Completed in-house 15 week academy training on Full Stack Development (Spring, React, SQL, AWS).
		\item Immediately placed within the Retail-Consumer-Goods Sales Division after graduation. Provided rapid prototyping 		capabilities to clients and spearheaded RCG to start transitioning off of PPT/PDF demos.
		\item Created and iterated over a next generational e-commerce Retail/Beauty Application. Utilized Media pipe libraries to combine retail use-cases with facial tracking and gesture based interactions.
		\item Managed several different projects utilizing NFC/GeoTech, D3 Data Visualization, and WebXR applications with \\ our Cognizant India and Netherlands teams.
		\item Owned products by leading team demos and stand ups with clients, upper management, and upper BU executives.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

	\begin{rSubsection}{Us. We. Together.}{January 2024 - March 2024}{Tech Lead}{Denver, CO}
		\item Tech Lead for the "Us. We. Together." Movement that envisions a future where health care workers thrive in safe, supportive, and empowering work environments. 
		\item Developed/Deployed a responsive Brand Hub and blog using React and Tailwind CSS for rapid styling and seamless mobile integration, while also launching the merchandise site built on WordPress.
	\end{rSubsection}

	\begin{rSubsection}{Tun3rs R US}{}{}{}
		\item Crafted a high-performance E-commerce platform for auto enthusiasts worldwide using Springboot, MongoDB, React, 	Axios, deployed on Beanstalk and Amplify.
	\end{rSubsection}

%------------------------------------------------
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    \textbf{Arizona State University}  \\ 
	M.S.E. in Software Engineering. \hfill \textit{August 2023 - Present} \\
	B.S. in Software Engineering, cum laude. \hfill \textit{August 2017 - May 2021} \\
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Technologies & Java, Spring Boot, JavaScript/Typescript, React, JSON, REST, AWS, MySQL
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
