%-------------------------
% Rover Resume - Milky Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass{article}

\usepackage{charter}
\usepackage{tgadventor}
\usepackage[letterspace=100]{microtype}
\usepackage{soul}

\usepackage[margin=1.3in,bottom=1.0in]{geometry}
\setcounter{secnumdepth}{0}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{4ex}{1ex}
\titlespacing{\subsection}{0pt}{*1}{*0.5}
\titlespacing{\subsubsection}{0pt}{*0.5}{*1}
\titleformat*{\section}{\titlerule\smallskip\footnotesize\sffamily\bfseries\lsstyle\uppercase}
\titleformat*{\subsection}{\Large}
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{left=0pt..2em,itemsep=0pt}

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							

\begin{document}
	\begin{center}
    {\sffamily\LARGE\bfseries \so{Alex A. Anguiano}} \par\bigskip
		\sffamily\footnotesize \so{https://www.linkedin.com/in/alex-a-anguiano/} \\ \medskip
		\so{(480) 335 2816 \quad alexanguiano96@gmail.com} \par
	\end{center}
	
\section{Work Experience}
	\subsection{Colorado Legislative Council \hfill Oct 2022 – Present}
	\subsubsection{Associate Application Developer $\rightarrow$ Application Developer} 
      	\begin{itemize}
      		\item Developed and maintained critical web applications for the Colorado State Legislature, while streamlining legislative processes and reducing third-party costs. Key accomplishments include:
      		\begin{itemize}
      			\item Implemented an advanced rich text editor (SunEditor) with history tracking, improving document creation efficiency for legislative staff.
      			\item Automated the generation of Colorado Red Books and revised statutes (Apache POI \& iText7), enabling on-demand access and facilitating legal review.
      			\item Replaced a legacy Microsoft Access system for the Joint Budget Committee, enabling the creation and management of the state's annual budget through a modern interface (React \& Java Spring).
      		\end{itemize}
      		\item Managed the full technology stack, from setting up on-premise servers, curating \& migrating databases, and CI/CD pipelines utilizing Bitbucket and Jenkins.
      	\end{itemize}
	
	\subsection{Cognizant \hfill June 2021 - Oct 2022}
	\subsubsection{Associate Full Stack Developer}
	\begin{itemize}
		\item Transformed the Retail-Consumer-Goods Sales Division's client presentations by introducing interactive prototypes, leading to more engaging and effective sales engagements.
		\item Developed a cutting-edge e-commerce Retail/Beauty application featuring virtual try-on capabilities using Mediapipe and 3.js, enhancing the online shopping experience.
		\item Successfully delivered multiple complex projects integrating NFC/GeoTech, D3 data visualization, and WebXR technologies, collaborating effectively with international teams.
		\item Effectively communicated project vision and progress to diverse audiences, including clients, upper management, and business unit executives, ensuring stakeholder buy-in and project success.
	\end{itemize}

\section{Education}
	\subsection{Arizona State University}
		\begin{itemize}
			\item M.S.E. in Software Engineering August 2023-Present.
			\item B.S. in Software Engineering, cum laude, August 2017-May 2021.
		\end{itemize}

\section{Technologies}
	\subsubsection{Java, Spring Boot, JavaScript/Typescript, React, JSON, REST, AWS, MySQL, MSSQL Server}
\end{document}
